Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-22 extended_catalog/paper/extended_catalog.tex
more plots

\begin{abstract}
We present a new method for analyzing 
the spatial extension of sources with
the Large Area Telescope (LAT), the primary science instrument on the
{\em \fermi Gamma-ray Space Telescope} (\fermi). 
Spatial extension
is an important input to correctly 
associate LAT sources with their counterparts at other
wavelengths. We perform
a series of Monte Carlo studies to validate this tool and calculate
the LAT's detection threshold to detect the extension of 
spatially extended sources.  We then
apply this tool to test all sources in the two year source catalog for
extension. We report the detection of nine spatially extended sources
in addition to the twelve spatially extended sources reported in the
second \fermi-LAT Catalog (2FGL).
\end{abstract}

@@

The Large Area Telescope (LAT) is a pair conversion telescope on the {\em \fermi
Gamma-Ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
sky since 2008 June.  The LAT has a broad energy coverage (20 \mev to $>300$
\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
($\sim 8000 \cm^2$ at $>1 \gev$).

Using two years of all-sky surveying data, the LAT Collaboration published
a catalog of 1873 \gev sources \citep{second_cat}. Many of these can be
positionally associated with a variety of source classes including Active
Galactic Nuclei (AGN), pulsars, galaxies, and supernova remnants (SNRs).
While the counterparts of many LAT sources
can be spatially resolved when observed
at other frequencies, detection of an extension at \gev energies by
the LAT is complicated by the large point-spread function (PSF)
of the instrument. The angular resolution for events converting in the
thin conversion foils of the tracker system, defined as the 68\% containment radius for
a point source, is approximately $3.5^{\circ}$ at 100 \mev, improving
to about 0.1$^{\circ}$ at 10 \gev.

>>>>

\begin{abstract}
We present a new method for quantifying
the spatial extension of sources with
the Large Area Telescope (LAT), the primary science instrument on the
{\em \fermi Gamma-ray Space Telescope} (\fermi). 
Spatial extension
is an important characteristic for correctly 
associating LAT sources with their counterparts at other
wavelengths. We perform
a series of Monte Carlo studies to validate this tool and calculate
the LAT's threshold for detecting the spatial extension of sources.  We then
use this tool to test all sources in the two year source catalog for
extension. We report the detection of nine spatially extended sources
in addition to the twelve spatially extended sources reported in the
second \fermi-LAT Catalog (2FGL).
\end{abstract}

@@

The Large Area Telescope (LAT) is a pair conversion telescope on the {\em \fermi
Gamma-ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
sky since 2008 June.  The LAT has broad energy coverage (20 \mev to $>300$
\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
($\sim 8000 \cm^2$ at $>1 \gev$).

Using two years of all-sky surveying data, the LAT Collaboration published
a catalog of 1873 \gev sources \citep{second_cat}. Many of these have been
positionally associated with a variety of source classes including Active
Galactic Nuclei (AGN), pulsars, galaxies, and supernova remnants (SNRs).
While the counterparts of many LAT sources
can be spatially resolved when observed
at other frequencies, detection of an extension at \gev energies by
the LAT is complicated by the large point-spread function (PSF)
of the instrument. The angular resolution for events converting in the
thin conversion foils of the tracker system, defined as the 68\% containment radius for
a point source, is approximately $3.5^{\circ}$ at 100 \mev, improving
to about 0.1$^{\circ}$ at 10 \gev.
